\section*{Appendix: Feedback Summary}
\addcontentsline{toc}{section}{Appendix A: Feedback Summary}
The feedback from the first peer mentioned some errors with grammar and sentence flow.
They annotated the report to point out these errors, most of which I agreed with and fixed.
One comment I did not agree with is that the reviewer mentioned not capitalizing the word Internet in the Introduction and Background section, where I write ``the Internet''.
I argue that this should stay capitalized because I am referring to the Internet as a proper noun, not as an adjective.
The reviewer also noted that I did not include a List of Figures section, so I added that.

The feedback from the second peer was not very descriptive, as they basically just said to include more information and topics.
However, after reading my report over, I identified that there may be a lack of evidence.
To fix this, I found a study on machine learning's use in detecting phishing attempts, and included that as a subsection of the evidence section in the main topics.

The feedback from the third peer was very short and vague.
They said to add more pictures within the text, which I agreed with and added a diagram of a reactive vs. proactive approach to cybersecurity.
The only other piece of feedback was that there were grammar errors, without telling me where they were.
Luckily, the feedback from the first peer highlighted many of the grammatical errors, and I was able to find some myself, so the grammar of this report was improved in this revision process.
