\begin{thebibliography}{99}
    \bibitem{winder2020}
    D. Winder, ``The University Of California Pays \$1 Million Ransom Following Cyber Attack,''
    \textit{forbes.com}, Jun. 29, 2020. [Online].
    Available: \href{https://www.forbes.com/sites/daveywinder/2020/06/29/the-university-of-california-pays-1-million-ransom-following-cyber-attack/?sh=5628ae8618a8}{https://www.forbes.com/sites/daveywinder/2020/06/29/the-university-of-california-pays-1-million-ransom-following-cyber-attack/?sh=5628ae8618a8}
    [Accessed March 6, 2022].

    \bibitem{microsoft2016}
    Microsoft Secure Blog Staff, ``The Emerging Era of Cyber Defense and Cybercrime,''
    \textit{Microsoft}, Jan. 27, 2016. [Online].
    Available: \href{https://www.microsoft.com/security/blog/2016/01/27/the-emerging-era-of-cyber-defense-and-cybercrime/}{https://www.microsoft.com/security/blog/2016/01/27/the-emerging-era-of-cyber-defense-and-cybercrime/}
    [Accessed March 7, 2022].

    \bibitem{morgan2020}
    S. Morgan, ``Cybercrime To Cost The World \$10.5 Trillion Annually By 2025,''
    \textit{cybersecurityventures.com}, Nov. 13, 2020. [Online].
    Available: \href{https://cybersecurityventures.com/cybercrime-damages-6-trillion-by-2021/}{https://cybersecurityventures.com/cybercrime-damages-6-trillion-by-2021/}
    [Accessed March 7, 2022].

    \bibitem{sarker_kayes_badsha_2020}
    I.H. Sarker, A.S.M. Kayes, S. Badsha, ``Cybersecurity data science: an overview from machine learning perspective,''
    J Big Data, Jul. 1, 2020. [Online].
    Available: \href{https://doi.org/10.1186/s40537-020-00318-5}{https://doi.org/10.1186/s40537-020-00318-5}
    [Accessed February 28, 2022].

    \bibitem{xin2018}
    Y. Xin et al., ``Machine Learning and Deep Learning Methods for Cybersecurity,''
    \textit{IEEE Access}, vol. 6, pp.3 5365-35381, 2018. [Online].
    Available: \href{https://ieeexplore.ieee.org/abstract/document/8359287/citations?tabFilter=papers}{https://ieeexplore.ieee.org/abstract/document/8359287/citations?tabFilter=papers}
    [Accessed March 7, 2022].

    \bibitem{echosec}
    Echosec Systems, ``How Is Machine Learning Used in Cybersecurity?,''
    \textit{Echosec Systems}. [Online].
    Available: \href{https://www.echosec.net/blog/how-is-machine-learning-used-in-cybersecurity}{https://www.echosec.net/blog/how-is-machine-learning-used-in-cybersecurity}

    \bibitem{microsoft2018}
    Microsoft Defender Security Research Team, ``How artificial intelligence stopped an Emotet outbreak,''
    \textit{Microsoft}, Feb. 14, 2018. [Online].
    Available: \href{https://www.microsoft.com/security/blog/2018/02/14/how-artificial-intelligence-stopped-an-emotet-outbreak/}{https://www.microsoft.com/security/blog/2018/02/14/how-artificial-intelligence-stopped-an-emotet-outbreak/}
    [Accessed March 7, 2022].
\end{thebibliography}
